\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{flushleft}
\textbf{\today}
\end{flushleft}

\vspace{1em}

\textbf{Muhammad Shafeen} \\
Deep learning Engineer
Pakistan \\

\vspace{2em}

\textbf{Mr. Zeeshan Khan} \\
Head of Deep Learning \\
Innotech Solutions\\
Islamabad , Pakistan.

\vspace{2em}

\textbf{Dear Mr. Khan,}

\vspace{1em}

\noindent
I am writing to express my interest in the Deep Learning position at [Company/Organization Name]. With a strong academic background in Artificial Intelligence from Fast National University of Computer and Emerging Sciences and hands-on experience in AI research and development, I am excited about the opportunity to contribute to your team.

During my internship at Innotech Solutions Pakistan, I developed and optimized AI models, including YOLO-based object detection and custom language models. My role involved integrating machine learning models into Android applications, which enhanced my skills in both deep learning and software development. Additionally, my experience as a Game Programmer Intern at M-Labs Remote allowed me to lead the development of gameplay mechanics and collaborate effectively within a team environment.

As a Data Structures Teaching Assistant at FAST National University, I honed my abilities in grading, student communication, and time management. My technical skills include proficiency in Deep Learning frameworks (CNN, VGG16, YOLO), Python (Pandas, PyTorch, NumPy, Scikit-learn), and experience with various programming languages such as C/C++, HTML/CSS, SQL, and Assembly. I am also familiar with tools like Git, Flutter, and LaTeX, which I have utilized in multiple projects.

One of my notable projects includes the development of a University Management System in C++ and a Weather Data Analysis tool using Python. These projects have strengthened my problem-solving skills and my ability to apply theoretical knowledge to practical applications.

I am passionate about advancing in the field of Deep Learning and am eager to bring my expertise to [Company/Organization Name]. I am confident that my background and skills make me a strong candidate for this position.

Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to your team.

\vspace{2em}

\textbf{Sincerely,}

\vspace{1em}

Muhammad Shafeen \\
BSc in Artificial Intelligence \\
Fast National University of Computer and Emerging Sciences, Peshawar

\end{document}
