\documentclass{article}
\usepackage{amsmath}

\begin{document}

\title{English Exercises Solutions}
\author{Your Name}
\date{\today}
\maketitle

\section*{Part 1: Identifying Underlined Words}

\begin{enumerate}
    \item Loudly \underline{knocking} at the gate, he demanded admission. \textbf{(Present Participle)}
    \item \underline{Deceived} by his friends, he lost all hopes. \textbf{(Past Participle)}
    \item We saw a few trees \underline{laden} with fruit. \textbf{(Past Participle)}
    \item Would you like to \underline{come} with me to the gym? \textbf{(Infinitive)}
    \item \underline{Hunting} tigers is a favourite sport in this country. \textbf{(Gerund)}
    \item We were prevented from \underline{seeing} the prisoner. \textbf{(Gerund)}
    \item His tattered coat needs \underline{mending}. \textbf{(Gerund)}
    \item Most people prefer to \underline{spend} their money rather than saving it. \textbf{(Infinitive)}
    \item He was reputed to be the most \underline{learned} man of his time. \textbf{(Past Participle)}
    \item The rain came \underline{pouring} down in torrents. \textbf{(Present Participle)}
    \item \underline{Hearing} a noise, I turned round. \textbf{(Present Participle)}
    \item \underline{Seizing} him by the arm, his friend led him. \textbf{(Present Participle)}
    \item It isn't good for you to \underline{eat} so many chocolates. \textbf{(Infinitive)}
    \item The \underline{making} of the plan is in hand. \textbf{(Gerund)}
    \item The indiscriminate \underline{reading} of novels is injurious. \textbf{(Gerund)}
    \item The enemy \underline{beaten} at every point, fled from the field. \textbf{(Past Participle)}
    \item She didn't like to \underline{leave} the children alone, but she had no choice. \textbf{(Infinitive)}
    \item Lessons \underline{learned} easily are soon forgotten. \textbf{(Past Participle)}
    \item We saw a clown \underline{standing} on his head. \textbf{(Present Participle)}
    \item He decided to \underline{put} his jacket on the hanger. \textbf{(Infinitive)}
    \item \underline{Jumping} over the fence, the thief escaped. \textbf{(Present Participle)}
    \item I used to \underline{go} to the cinema a lot. \textbf{(Infinitive)}
    \item \underline{Walking} on the grass is forbidden. \textbf{(Gerund)}
    \item \underline{Waving} their hats and handkerchiefs, the people cheered the king. \textbf{(Present Participle)}
    \item The miser hated \underline{spending} money. \textbf{(Gerund)}
    \item I'm not used to \underline{get up} this early. \textbf{(Infinitive)}
    \item \underline{Being occupied} with important matters, he had no leisure to see us. \textbf{(Present Participle)}
    \item \underline{Driven} by hunger, he stole a piece of bread. \textbf{(Past Participle)}
    \item \underline{Singing} to herself was her chief delight. \textbf{(Gerund)}
    \item \underline{Praising} all alike is \underline{praising} none. \textbf{(Gerund)}
\end{enumerate}

\textbf{Related Examples for Exam:}
\begin{itemize}
    \item The \underline{broken} vase lay on the floor. \textbf{(Past Participle)}
    \item \underline{Swimming} is my favorite hobby. \textbf{(Gerund)}
    \item She loves to \underline{dance}. \textbf{(Infinitive)}
    \item \underline{Running} late, he missed the bus. \textbf{(Present Participle)}
\end{itemize}

\section*{Part 2: Correct Form of the Verbs}

\begin{enumerate}
    \item They (not go) \textbf{do not go} to the zoo very often.
    \item I (not be) \textbf{will not be} at home next Monday evening.
    \item Her father (work) \textbf{works} from the morning till night every day.
    \item Mr. Robinson (look) \textbf{is looking} for an apartment at present.
    \item There (be) \textbf{are} a few empty apartments near his office.
    \item Hoa's parents love (work) \textbf{working} on their farm.
    \item Is it easy (find) \textbf{to find} an apartment in Ha Noi?
    \item Please tell her I (call) \textbf{will call} again later.
    \item My best friend (come) \textbf{is coming} here soon.
    \item My father (not drink) \textbf{does not drink} coffee in the evening.
    \item I usually (go) \textbf{go} to school by bike but tomorrow I (catch) \textbf{will catch} a bus to school.
    \item Listen! Jane (play) \textbf{is playing} the piano.
    \item We (not go) \textbf{are not going} fishing this weekend. We (go) \textbf{are going} sailing.
    \item What (do) \textbf{does} your mother (do) \textbf{do} now? - She (cook) \textbf{is cooking}.
    \item I'd like (visit) \textbf{to visit} Japan some days.
    \item What about (take) \textbf{taking} a taxi?
\end{enumerate}

\textbf{Related Examples for Exam:}
\begin{itemize}
    \item She (read) \textbf{reads} a book every night.
    \item They (go) \textbf{are going} to the park tomorrow.
    \item He (not like) \textbf{does not like} vegetables.
    \item We (visit) \textbf{visited} our grandparents last weekend.
\end{itemize}

\section*{Part 3: Conditionals}

\begin{enumerate}
    \item If I had time, I (do) \textbf{would do} shopping with you.
    \item If you (speak) \textbf{speak} English, you will get along with them perfectly.
    \item If they had gone for a walk, they (turn) \textbf{would have turned} the lights off.
    \item If he had known all the facts, he (not be) \textbf{would not have been} so angry.
    \item If he (put out) \textbf{had put out} the fire, he wouldn't have been so hot.
    \item I wouldn't have eaten it if I (know) \textbf{had known} that there was garlic in it.
    \item I (take) \textbf{would have taken} a taxi if I had known that it was such a long way.
    \item If she (come) \textbf{comes} to see us, we will go to the zoo.
    \item I would have told you if I (see) \textbf{had seen} him.
    \item Would you mind if I (open) \textbf{opened} the window?
    \item If they (invite) \textbf{had invited} me, I wouldn't have said no.
    \item My friend (meet) \textbf{will meet} me at the station if he gets the afternoon off.
    \item If I (not do) \textbf{do not do} it, nobody would do it.
    \item If my father (not pick) \textbf{had not picked} me up, I'll take the bus home.
    \item If I hadn't been so silly, I (earn) \textbf{would have earned} a lot of money.
    \item If she (speak) \textbf{spoke} more slowly, everybody would have understood her.
    \item If she had listened to my directions, she (not get lost) \textbf{would not have got lost}.
    \item If you had arrived earlier, you (see) \textbf{would have seen} me on TV.
    \item If they (have) \textbf{have} time at the weekend, they will come to see us.
    \item I would not have read your diary if you (not hide) \textbf{had not hidden} it in such an obvious place.
    \item If I (be) \textbf{were} you, I would not buy that dress.
    \item If I (tell) \textbf{told} you a secret, you would be sure to leak it.
    \item We (arrive) \textbf{would have arrived} earlier if we had not missed the bus.
    \item You wouldn't have got into trouble if you (listen) \textbf{had listened} to me.
    \item If I had tried again, I think that I (be) \textbf{would be} successful.
    \item If I had known you were coming, I (make) \textbf{would have made} a cake.
    \item If I had been there, I (not do) \textbf{would not have done} it.
    \item If I had been ready when he phoned, he (take) \textbf{would have taken} me with them.
    \item If I (know) \textbf{had known} what a bad driver you were, I wouldn't have come with you.
    \item If I (have) \textbf{had} a map, I would be O.K.
    \item If I didn't have a mobile phone, my life (not be) \textbf{would not be} complete.
    \item If we (know) \textbf{had known} about your problem, we would have helped you.
    \item If we sneak out quietly, nobody (notice) \textbf{will notice}.
    \item If you had put some vegetables in the sandwiches, they (taste) \textbf{would have tasted} better.
    \item If you had told me everything about him, I (not tell) \textbf{would not tell} him anything.
    \item If you had told me that, I (not lend) \textbf{would not have lent} him any money.
    \item If you weren’t so selfish, we (have) \textbf{would have} a house.
    \item Okay, I (get) \textbf{will get} the popcorn if you buy the drinks.
    \item She (go) \textbf{would go} out with you if you had only asked her.
    \item The burglars wouldn't have got in if you (close) \textbf{had closed} the door.
\end{enumerate}

\textbf{Related Examples for Exam:}
\begin{itemize}
    \item If I (know) \textbf{had known} the answer, I would have told you.
    \item If you (study) \textbf{study} hard, you will pass the exam.
    \item If he (be) \textbf{were} taller, he could reach the top shelf.
    \item If they (not be) \textbf{had not been} late, we would have caught the train.
\end{itemize}

\end{document}
