\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{ragged2e} % Package for justified text

% Title Section
\title{Statement of Purpose}
\author{Muhammad Shafeen (22P-9278)}
\date{}

\begin{document}

\maketitle

\doublespacing
\justifying % Justifies the entire document


My name is Muhammad Shafeen, and I am from Pakistan. I completed my Bachelor's degree in Artificial Intelligence from the National University of Computer and Emerging Sciences (NUCES), Peshawar. During my undergraduate studies, I actively participated in various projects related to Artificial Intelligence (AI) and Computer Vision, which further strengthened my passion for these fields.

After completing my higher education, I had the opportunity to intern at a renowned software company for three months. During this internship, I worked on real-world projects related to AI, which further deepened my interest in Computer Vision. The experience helped me understand the practical applications of AI technologies, especially in the domain of visual data processing and analysis. I have also been working as an AI Engineer, where I actively contribute to developing innovative solutions using Computer Vision techniques.

I have a strong interest in pursuing a Master's degree in Computer Vision, which has become a prominent field in modern AI research. I am particularly fascinated by the work of David Marr, whose contributions to the understanding of visual perception have had a lasting impact on the field. My work on several Computer Vision projects, including the detection of fighter jets and tanks using AI models, has further fueled my passion for this emerging area. These projects have not only provided me with technical expertise but have also instilled in me the drive to explore new challenges and contribute to the advancement of this field.

I am particularly interested in pursuing my Master's at the University of London, a world-renowned institution known for its outstanding research and teaching standards in the field of Artificial Intelligence and Computer Vision. The University's emphasis on cutting-edge technology, combined with its focus on real-world applications, makes it an ideal place for me to expand my knowledge and skills. I believe that studying at the University of London will provide me with the academic rigor and exposure to innovative research that will allow me to excel in this field.

Through this program, I aim to continue my journey of learning and innovation, contributing to AI's progress while developing solutions that can make a meaningful impact on society. After completing my Master’s, I am eager to return to my country and apply the advanced knowledge and skills I acquire to address local challenges. I believe that leveraging AI and Computer Vision technologies can drive significant advancements in Pakistan, particularly in areas such as healthcare, security, and education. I am excited about the prospect of collaborating with like-minded professionals and researchers to push the boundaries of what AI can achieve, both globally and in my home country, to create transformative solutions that benefit society.

\end{document}
