%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Structure Teacher Assisstant} % Job title
    {FAST National Univeristy Of Computer And Emerging Sciences} % Organisation
    {Pakistan} % Location
    {Sept 2020 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped With checking student's quizzes and assignments}
        \item {Learned dealing with students with respect to different aspects}
        \item {\textbf{Soft Skills:} Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
     \cventry
    {AI Research and Development Intern} % Job title
    {Innotech Solutions} % Organisation
    {Pakistan} % Location
    {July 2024 - August 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and optimized a range of AI models, including YOLO-based object detection, face recognition, and custom LLMs using MediaPipe.}
        \item {Led the data collection and preprocessing efforts for various projects, including offline weather prediction and jet detection tasks.}
        \item {Integrated machine learning models into Android applications, ensuring efficient performance across different devices.}
        \item {Addressed challenges related to data accessibility, model optimization, and real-time deployment.}
        \item {\textbf{Technical Skills:} Python, TensorFlow, Android Studio, Google Colab, MediaPipe, YOLO, Data Scraping.}
        \item {\textbf{Soft Skills:} Problem-solving, Time Management, Adaptability, Collaboration.}
      \end{cvitems}
    }
    \cventry
    {Game Programmer Intern} % Job title
    {M-Labs} % Organisation
    {Remote, Lahore, Pakistan} % Location
    {June 2024 - August 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with a team of 3 members to design and develop a game named "Slingshot" from concept to deployment.}
        \item {Implemented core gameplay mechanics and optimized the game's performance for various platforms.}
        \item {Led the development of game physics, player controls, and UI/UX elements to ensure an engaging user experience.}
        \item {Worked on bug fixing, feature enhancements, and performed code reviews to maintain code quality.}
        \item {Conducted playtesting sessions and gathered user feedback to iteratively improve game design.}
        \item {\textbf{Technical Skills:} Unity, C#, Game Physics, UI/UX Design, Git, Remote Collaboration Tools.}
        \item {\textbf{Soft Skills:} Teamwork, Communication, Creativity, Problem-solving, Time Management.}
      \end{cvitems}
    }

\end{cventries}
