%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {FAST NUCES} % Organisation
    {\href{https://github.com/shafeenyousafzaii/University-Management-System-with-C-}{University Management System ( C++) | OOP }   } % Project
    {Pakistan} % Location
    {Jan 2023 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Created a terminal-based university management system using OOP concepts }
\        \item {\textbf{Technical Skills:} C++ , VS code , Draw.io .}
        \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Report writing.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {FAST NUCES} % Organisation
    {\href{https://github.com/shafeenyousafzaii/Weather-Data-Analysis-Project}{Weather Data Analysis ( Python ) – Predicts Weather }} % Project
    {Pakistan} % Location
    {Aug 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
      \item {Used \texttt{\textbf{ Scikit-learn}} for training the Machine learning model}
      % \item {Agents add noise to their outputs to maintain privacy while satisfying agent-level and system-level MTL specifications.}
      \item {Used \textbf{Linear Regression} from Sci-kit Learn}
      \item {Used \textbf{Function-Transformer} from Sci-kit Learn}
        \item {\textbf{Technical Skills:} Python with Pandas, sklearn, Seaborn , scikit-learn .}
        \item {\textbf{Soft Skills:} Presentation skills, Leadership, Teamwork, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {FAST NUCES} % Organisation
    {\href{https://github.com/shafeenyousafzaii/Pneumonia_Detection_Team_Project}{Pneumonia Detection With Scrap CNN and VGG16} } % Project
    {Pakistan} % Location
    {Aug 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a deep learning model using Convolutional Neural Networks (CNNs) and VGG16 for automated pneumonia detection from chest X-ray images.}
        \item {Implemented a web interface using HTML, CSS, JavaScript, and Flask to allow real-time analysis and user-friendly interaction for healthcare professionals.}
        \item {Fine-tuned the VGG model to improve performance, incorporating global pooling, fully connected, and dropout layers.}
        \item {\textbf{Technical Skills:} Python with CNN, seaborn, tensorflow, sklearn, scipy.}
        \item {\textbf{Soft Skills:} Report writing, logical thinking, critical thinking, teamwork.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FAST NUCES} % Organisation
  {\href{https://github.com/shafeenyousafzaii/University-Management-System-And-Student-Services}{University Management System And Student Services With Database } } % Project
    {Pakistan} % Location
    {Jan 2024 - May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a full fledge Website hosted locally , integrated with database using Mysql }
        \item {\textbf{Technical Skills:} Mysql server , Microsoft Workbench , PHP , HTML , CSS , Javascript}
        \item {\textbf{Soft Skills:} Report writing, Logical Thinking, Critical Thinking , team work.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
