\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{flushleft}
\today
\end{flushleft}

\vspace{1em}

Kashif Khan \\
22P-9005

\vspace{2em}

Miss Noureen Shah \\
Subject Coordinator  \\
FAST NUCES \\
Peshawar

\vspace{2em}

\textbf{Dear Sir,}

\vspace{1em}

\noindent
\textbf{Subject: Proposal to Extend Library Operating Hours}

\vspace{1em}

Over the past semester, many students, including myself, have found it challenging to access quiet study spaces during late evening hours. With increasing academic demands and varied personal schedules, the need for extended library hours has become more apparent.

\vspace{1em}

Our library is a vital resource that supports our academic success. Extending its operating hours until midnight on weekdays would greatly benefit students who prefer studying later in the day due to classes, part-time jobs, or other commitments. This change would provide a conducive environment for focused study and research, enhancing overall academic performance.

\vspace{1em}

Universities that have adopted extended library hours have reported positive feedback from students and a noticeable improvement in academic results. Implementing this adjustment at FAST NUCES could position our institution as responsive to student needs and committed to academic excellence. I've gathered feedback from fellow students who strongly support this proposal, and I am willing to assist in any way to facilitate this change.

\vspace{1em}

I kindly request the opportunity to discuss this proposal with you at your earliest convenience. Your consideration of this matter is greatly appreciated, and I believe it could significantly enhance the student experience on our campus. Please let me know if we could meet next week to explore this possibility further.

\vspace{2em}

\textbf{Regards,}

\vspace{1em}

Kashif Khan \\
22P-9005

\end{document}